---
title: "visualization_1"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
```

**Importing Data**

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") %>% 
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>% 
  select(name, id, everything())
```

**First Plot**

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

```{r}
gg_weather_scatterplot <- 
  weather_df %>%  
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
gg_weather_scatterplot
```

**Checking why rows are missing**

```{r}
weather_df %>% 
  filter(is.na(tmax))
```

## Fancier Scatterplot 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.3, size = 0.8) + 
  geom_smooth(se = FALSE)
```

- alpha makes the points transparent

- size scales the points to make them larger/smaller

- geom_smooth gives a smooth curve fit through the scatterplot 

  - se is standard error bars 

**Where you define aesthetics can matter**

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = 0.3, size = 0.8) + 
  geom_smooth(se = FALSE)
```

- Only get one smooth curve 

- aes() defines the color for only the points and then geom smooth doesn't 
understand the color

- If you put aes() in the ggplot() definition makes the color defined everywhere

**Use* faceting**

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

- Facet splits the data into different plots

**More Interesting Scatterplot**

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name, size = prcp)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

- Can see the seasonal trend because the x axis is date 

- When the dots are large, this means there is more precipitation

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(tmin, 
         tmin_f = tmin * (9/5) + 32) %>% 
  mutate(tmax, tmax_f = tmax * (9/5) + 32) %>% 
  ggplot(aes(x = tmin_f, y = tmax_f)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
  
```

- Can change the method that geom_smooth uses with the method argument

## Small Things 

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_smooth(se = FALSE) 
```

- Can just create the line

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_hex()
```

- Makes a hex plot 

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax, color = "blue")) + 
  geom_point()
```

- Tries to create a variable named blue and color the points that color 

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(color = "blue")
```

- Changes the color of all the points 

# Univariate Plots 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge")
```

- Creates a histogram, but is hard to read

**How to fix this**

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram() + 
  facet_grid(.~name)
```

**Density Plot**

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = 0.3)
```

- Like a smoothed histogram


**Box Plot**

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_boxplot()
```

**Violin Plots**

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin()
```

- Takes the density and flips it  to make it vertical

**Ridge Plots**

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) + 
  geom_density_ridges()
```

- Each density is separated vertically

**Example**

```{r}
weather_df %>% 
  ggplot(aes(x = prcp, fill = name)) + 
  geom_density(alpha = 0.3)

weather_df %>% 
  ggplot(aes( x = name, y = prcp)) + 
  geom_boxplot()

weather_df %>% 
  filter(prcp > 10) %>% 
  ggplot(aes(x = prcp, fill = name)) + 
  geom_density(alpha = 0.3)
```

## Saving and embedding plots

**Saving Plots**
```{r}
ggp_weather <- 
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point()

ggsave("ggp_weather.pdf", ggp_weather, width = 8, height = 6)
```

**Embedding Plots**

```{r, fig.width = 6, fig.asp = 0.6}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point()
```

- Can change the width and height of the plot